Determinism, Complexity, and Predictability in Computer Performance

### 2014-02-27 pecomplexity.tex
Fixing pecomplexity.tex
sig figs and rearrange table

\newtheorem*{mydef}{Definition}
\title{Determinism, Complexity, and Predictability in Computer Performance\\
Quantifying structured complexity and its role in predictability: With applications to predicting computer performance.
\\ Quantifying Predictability through Structural Complexity
\\ Quantifying Predictability using Structural Complexity
}

@@

\input{intro.tex}

\input{methods.tex}

@@

>>>>

\newtheorem*{mydef}{Definition}
\title{Determinism, Complexity, and Predictability in Computer Performance\\
Quantifying structured complexity and its role in predictability: With applications to predicting computer performance.
\\ Quantifying Predictability through Structural Complexity \\
{\color{green}Quantifying Predictability through Structural Complexity} 
\\ Quantifying Predictability using Structural Complexity 
\\Decoding Predictability in Complicated Real-Valued Time Series: The balance between complexity and temporal structure
\\Decoding Complicated Time Series: The balance between complexity and temporal structure and the implications for predictability
}

@@

\input{intro.tex}
\input{related.tex}
\input{methods.tex}

@@

\section{Appendix}

\begin{table}[h]
  \begin{center}
  \begin{tabular}{|c|c|c|c|c|}
  \hline
            & MASE LMA    & MASE ARIMA &MASE na\"{i}ve   & $l=6$ \\
 \hline

 \col           & $ 0.050 \pm0.002  $ & $0.599  \pm 0.211 $ & $0.571\pm0.002$&  $0.513 \pm 0.003$ \\

\gcc           & $ 1.530\pm 0.021$ & $1.837 \pm0.016 $ & $0.951 \pm 0.001$ & $0.943 \pm 0.001$ \\

\svdone     & $ 0.827\pm 0.076$ & $ 0.714\pm 0.075 $ & $2.676\pm4.328$&  $0.957 \pm 0.016$ \\

 \svdtwo    & $1.279 \pm0.020 $ & $2.163 \pm0.027 $ &  $3.054\pm0.040$ &   $0.846 \pm0.004$ \\

 \svdthree     & $0.619 \pm0.021 $ & $0.713 \pm 0.010 $ & $31.386\pm 0.282$ &  $0.716 \pm 0.006$ \\

 \svdfour     & $ 0.779\pm0.036 $ & $0.979 \pm0.032 $ & $2.661\pm0.074$ & $0.825 \pm 0.008$ \\

 \svdfive     & $ 0.718\pm 0.048 $ & $2.370  \pm 0.051 $ & $20.870 \pm 0.192$&  $0.678 \pm 0.007$ \\

 \svdsix     & $ 0.739\pm 0.068 $ & $ 1.438\pm 0.0610$ & $2.197\pm0.083$&  $0.748 \pm 0.011$ \\
  \hline
  \end{tabular}
  \end{center}
 \label{default}
 \caption{Detailed MASE scores}
 \label{tab:error}
  \end{table}%
